\hypertarget{chirp-1330-interface-specification}{%
\section{CHIRP 1330 Interface
Specification}\label{chirp-1330-interface-specification}}

Interface Specification Version 02.02.07

12-17-2020

\hypertarget{global-groups}{%
\subsection{Global Groups}\label{global-groups}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Path & Description\tabularnewline
\midrule
\endhead
/ & User data\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{global-dimensions}{%
\subsection{Global Dimensions}\label{global-dimensions}}

\begin{longtable}[]{@{}lll@{}}
\toprule
Name & Size & Description\tabularnewline
\midrule
\endhead
fov & 9 & Field-of-view dimension\tabularnewline
obs & 12,150 & number of spectra in 6-minute L1 CHIRP for the 13:30
orbit. 135*90 or 45*30*9\tabularnewline
wnum & 1,679 & IR channel number\tabularnewline
fov\_poly & 8 & lat\_bnds, lon\_bnds points defining the polygon
bounding an FOV (anticlockwise as viewed from above)\tabularnewline
utc\_tuple & 8 & parts of UTC time: year, month, day, hour, minute,
second, millisec, microsec\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{global-attributes}{%
\subsection{Global Attributes}\label{global-attributes}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Name & Type & Size & Value & Description\tabularnewline
\midrule
\endhead
keywords & string & 1 & EARTH SCIENCE \textgreater{}
SPECTRAL/ENGINEERING \textgreater{} INFRARED WAVELENGTHS \textgreater{}
INFRARED RADIANCE & A comma-separated list of key words and/or phrases.
Keywords may be common words or phrases, terms from a controlled
vocabulary (GCMD is often used), or URIs for terms from a controlled
vocabulary (see also "keywords\_vocabulary" attribute).\tabularnewline
Conventions & string & 1 & CF-1.6\textbackslash{}, ACDD-1.3 & A
comma-separated list of the conventions that are followed by the
dataset.\tabularnewline
history & string & 1 & & Provides an audit trail for modifications to
the original data. This attribute is also in the NetCDF Users Guide:
'This is a character array with a line for each invocation of a program
that has modified the dataset. Well-behaved generic netCDF applications
should append a line containing: date, time of day, user name, program
name and command arguments.' To include a more complete description you
can append a reference to an ISO Lineage entity; see NOAA EDM ISO
Lineage guidance.\tabularnewline
source & string & 1 & AIRS and CrIS instrument telemetry & The method of
production of the original data. If it was model-generated, source
should name the model and its version. If it is observational, source
should characterize it. This attribute is defined in the CF Conventions.
Examples: 'temperature from CTD \#1234'; 'world model
v.0.1'.\tabularnewline
processing\_level & string & 1 & 1 & A textual description of the
processing (or quality control) level of the data.\tabularnewline
product\_name\_type\_id & string & 1 & L1 & Product name as it appears
in product\_name (L1A, L1B, L2, SNO\_AIRS\_CrIS)\tabularnewline
comment & string & 1 & & Miscellaneous information about the data or
methods used to produce it. Can be empty.\tabularnewline
acknowledgment & string & 1 & Support for this research was provided by
NASA. & A place to acknowledge various types of support for the project
that produced this data.\tabularnewline
license & string & 1 & Limited to Sounder SIPS affiliates & Provide the
URL to a standard or specific license, enter "Freely Distributed" or
"None", or describe any restrictions to data access and distribution in
free text.\tabularnewline
standard\_name\_vocabulary & string & 1 & CF Standard Name Table v28 &
The name and version of the controlled vocabulary from which variable
standard names are taken. (Values for any standard\_name attribute must
come from the CF Standard Names vocabulary for the data file or product
to comply with CF.) Example: 'CF Standard Name Table
v27'.\tabularnewline
date\_created & string & 1 & Unassigned & The date on which this version
of the data was created. (Modification of values implies a new version,
hence this would be assigned the date of the most recent values
modification.) Metadata changes are not considered when assigning the
date\_created. The ISO 8601:2004 extended date format is recommended, as
described in the Attribute Content Guidance section.\tabularnewline
creator\_name & string & 1 & Unassigned & The name of the person (or
other creator type specified by the creator\_type attribute) principally
responsible for creating this data.\tabularnewline
creator\_email & string & 1 & Unassigned & The email address of the
person (or other creator type specified by the creator\_type attribute)
principally responsible for creating this data.\tabularnewline
creator\_url & string & 1 & Unassigned & The URL of the person (or other
creator type specified by the creator\_type attribute) principally
responsible for creating this data.\tabularnewline
institution & string & 1 & Unassigned & Processing facility that
produced this file\tabularnewline
project & string & 1 & Sounder SIPS & The name of the project(s)
principally responsible for originating this data. Multiple projects can
be separated by commas, as described under Attribute Content Guidelines.
Examples: 'PATMOS-X', 'Extended Continental Shelf
Project'.\tabularnewline
product\_name\_project & string & 1 & SNDR & The name of the project as
it appears in the file name. 'SNDR' for all Sounder SIPS products, even
AIRS products.\tabularnewline
publisher\_name & string & 1 & Unassigned & The name of the person (or
other entity specified by the publisher\_type attribute) responsible for
publishing the data file or product to users, with its current metadata
and format.\tabularnewline
publisher\_email & string & 1 & Unassigned & The email address of the
person (or other entity specified by the publisher\_type attribute)
responsible for publishing the data file or product to users, with its
current metadata and format.\tabularnewline
publisher\_url & string & 1 & Unassigned & The URL of the person (or
other entity specified by the publisher\_type attribute) responsible for
publishing the data file or product to users, with its current metadata
and format.\tabularnewline
geospatial\_bounds & string & 1 & & Describes the data's 2D or 3D
geospatial extent in OGC's Well-Known Text (WKT) Geometry format
(reference the OGC Simple Feature Access (SFA) specification). The
meaning and order of values for each point's coordinates depends on the
coordinate reference system (CRS). The ACDD default is 2D geometry in
the EPSG:4326 coordinate reference system. The default may be overridden
with geospatial\_bounds\_crs and geospatial\_bounds\_vertical\_crs (see
those attributes). EPSG:4326 coordinate values are longitude (decimal
degrees\_east) and latitude (decimal degrees\_north), in that order.
Longitude values in the default case are limited to the {[}-180, 180)
range. Example: 'POLYGON ((-111.29 40.26, -111.29 41.26, -110.29 41.26,
-110.29 40.26, -111.29 40.26))'.\tabularnewline
geospatial\_bounds\_crs & string & 1 & EPSG:4326 & The coordinate
reference system (CRS) of the point coordinates in the
geospatial\_bounds attribute. This CRS may be 2-dimensional or
3-dimensional, but together with geospatial\_bounds\_vertical\_crs, if
that attribute is supplied, must match the dimensionality, order, and
meaning of point coordinate values in the geospatial\_bounds attribute.
If geospatial\_bounds\_vertical\_crs is also present then this attribute
must only specify a 2D CRS. EPSG CRSs are strongly recommended. If this
attribute is not specified, the CRS is assumed to be EPSG:4326.
Examples: 'EPSG:4979' (the 3D WGS84 CRS), 'EPSG:4047'.\tabularnewline
geospatial\_lat\_min & float & 1 & 9.9692099683868690e+36f & Describes a
simple lower latitude limit; may be part of a 2- or 3-dimensional
bounding region. Geospatial\_lat\_min specifies the southernmost
latitude covered by the dataset.\tabularnewline
geospatial\_lat\_max & float & 1 & 9.9692099683868690e+36f & Describes a
simple upper latitude limit; may be part of a 2- or 3-dimensional
bounding region. Geospatial\_lat\_max specifies the northernmost
latitude covered by the dataset.\tabularnewline
geospatial\_lon\_min & float & 1 & 9.9692099683868690e+36f & Describes a
simple longitude limit; may be part of a 2- or 3-dimensional bounding
region. geospatial\_lon\_min specifies the westernmost longitude covered
by the dataset. See also geospatial\_lon\_max.\tabularnewline
geospatial\_lon\_max & float & 1 & 9.9692099683868690e+36f & Describes a
simple longitude limit; may be part of a 2- or 3-dimensional bounding
region. geospatial\_lon\_max specifies the easternmost longitude covered
by the dataset. Cases where geospatial\_lon\_min is greater than
geospatial\_lon\_max indicate the bounding box extends from
geospatial\_lon\_max, through the longitude range discontinuity meridian
(either the antimeridian for -180:180 values, or Prime Meridian for
0:360 values), to geospatial\_lon\_min; for example,
geospatial\_lon\_min=170 and geospatial\_lon\_max=-175 incorporates 15
degrees of longitude (ranges 170 to 180 and -180 to
-175).\tabularnewline
time\_coverage\_start & string & 1 & & Nominal start time. Describes the
time of the first data point in the data set. Use the ISO 8601:2004 date
format, preferably the extended format as recommended in the Attribute
Content Guidance section.\tabularnewline
time\_of\_first\_valid\_obs & string & 1 & & Describes the time of the
first valid data point in the data set. Use the ISO 8601:2004 date
extended format.\tabularnewline
time\_coverage\_mid & string & 1 & & Describes the midpoint between the
nominal start and end times. Use the ISO 8601:2004 date format,
preferably the extended format as recommended in the Attribute Content
Guidance section.\tabularnewline
time\_coverage\_end & string & 1 & & Nominal end time. Describes the
time of the last data point in the data set. Use ISO 8601:2004 date
format, preferably the extended format as recommended in the Attribute
Content Guidance section.\tabularnewline
time\_of\_last\_valid\_obs & string & 1 & & Describes the time of the
last valid data point in the data set. Use the ISO 8601:2004 date
extended format.\tabularnewline
time\_coverage\_duration & string & 1 & P0000-00-00T00:06:00 & Describes
the duration of the data set. Use ISO 8601:2004 duration format,
preferably the extended format as recommended in the Attribute Content
Guidance section.\tabularnewline
product\_name\_duration & string & 1 & m06 & Product duration as it
appears in product\_name (m06 means six minutes)\tabularnewline
creator\_type & string & 1 & institution & Specifies type of creator
with one of the following: 'person', 'group', 'institution', or
'position'. If this attribute is not specified, the creator is assumed
to be a person.\tabularnewline
creator\_institution & string & 1 & Jet Propulsion Laboratory -\/-
California Institute of Technology & The institution of the creator;
should uniquely identify the creator's institution. This attribute's
value should be specified even if it matches the value of
publisher\_institution, or if creator\_type is
institution.\tabularnewline
product\_version & string & 1 & vxx.xx.xx & Version identifier of the
data file or product as assigned by the data creator. For example, a new
algorithm or methodology could result in a new
product\_version.\tabularnewline
keywords\_vocabulary & string & 1 & GCMD:GCMD Keywords & If you are
using a controlled vocabulary for the words/phrases in your "keywords"
attribute, this is the unique name or identifier of the vocabulary from
which keywords are taken. If more than one keyword vocabulary is used,
each may be presented with a prefix and a following comma, so that
keywords may optionally be prefixed with the controlled vocabulary key.
Example: 'GCMD:GCMD Keywords, CF:NetCDF COARDS Climate and Forecast
Standard Names'.\tabularnewline
platform & string & 1 & JPSS-1 \textgreater{} Joint Polar Satellite
System - 1\textbackslash{}, SUOMI-NPP \textgreater{} Suomi National
Polar-orbiting Partnership\textbackslash{}, AQUA \textgreater{} Earth
Observing System & Name of the platform(s) that supported the sensor
data used to create this data set or product. Platforms can be of any
type, including satellite, ship, station, aircraft or other. Indicate
controlled vocabulary used in platform\_vocabulary.\tabularnewline
platform\_vocabulary & string & 1 & GCMD:GCMD Keywords & Controlled
vocabulary for the names used in the "platform"
attribute.\tabularnewline
product\_name\_platform & string & 1 & SS1330 & Platform name as it
appears in product\_name\tabularnewline
instrument & string & 1 & AIRS \textgreater{} Atmospheric Infrared
Sounder\textbackslash{}, CrIS \textgreater{} Cross-track Infrared
Sounder & Name of the contributing instrument(s) or sensor(s) used to
create this data set or product. Indicate controlled vocabulary used in
instrument\_vocabulary.\tabularnewline
instrument\_vocabulary & string & 1 & GCMD:GCMD Keywords & Controlled
vocabulary for the names used in the "instrument"
attribute.\tabularnewline
product\_name\_instr & string & 1 & CHIRP & Instrument name as it
appears in product\_name\tabularnewline
product\_name & string & 1 & & Canonical fully qualified product name
(official file name)\tabularnewline
product\_name\_variant & string & 1 & std & Processing variant
identifier as it appears in product\_name. 'std' (shorthand for
'standard') is to be the default and should be what is seen in all
public products.\tabularnewline
product\_name\_version & string & 1 & vxx\_xx\_xx & Version number as it
appears in product\_name (v01\_00\_00)\tabularnewline
product\_name\_producer & string & 1 & T & Production facility as it
appears in product\_name (single character) 'T' is the default, for
unofficial local test products\tabularnewline
product\_name\_timestamp & string & 1 & yymmddhhmmss & Processing
timestamp as it appears in product\_name (yymmddhhmmss)\tabularnewline
product\_name\_extension & string & 1 & nc & File extension as it
appears in product\_name (typically nc)\tabularnewline
granule\_number & ushort & 1 & & granule number of day
(1-240)\tabularnewline
product\_name\_granule\_number & string & 1 & g000 & zero-padded string
for granule number of day (g001-g240)\tabularnewline
gran\_id & string & 1 & yyyymmddThhmm & Unique granule identifier
yyyymmddThhmm of granule start, including year, month, day, hour, and
minute of granule start time\tabularnewline
geospatial\_lat\_mid & float & 1 & 9.9692099683868690e+36f & granule
center latitude\tabularnewline
geospatial\_lon\_mid & float & 1 & 9.9692099683868690e+36f & granule
center longitude\tabularnewline
featureType & string & 1 & trajectory & structure of data in
file\tabularnewline
data\_structure & string & 1 & trajectory & a character string
indicating the internal organization of the data with currently allowed
values of 'grid', 'station', 'trajectory', or 'swath'. The 'structure'
here generally describes the horizontal structure and in all cases data
may also be functions, for example, of a vertical coordinate and/or
time. (If using CMOR pass this in a call to
cmor\_set\_cur\_dataset\_attribute.)\tabularnewline
cdm\_data\_type & string & 1 & Trajectory & The data type, as derived
from Unidata's Common Data Model Scientific Data types and understood by
THREDDS. (This is a THREDDS "dataType", and is different from the CF
NetCDF attribute 'featureType', which indicates a Discrete Sampling
Geometry file in CF.)\tabularnewline
id & string & 1 & Unassigned & An identifier for the data set, provided
by and unique within its naming authority. The combination of the
"naming authority" and the "id" should be globally unique, but the id
can be globally unique by itself also. IDs can be URLs, URNs, DOIs,
meaningful text strings, a local key, or any other unique string of
characters. The id should not include white space
characters.\tabularnewline
naming\_authority & string & 1 & Unassigned & The organization that
provides the initial id (see above) for the dataset. The naming
authority should be uniquely specified by this attribute. We recommend
using reverse-DNS naming for the naming authority; URIs are also
acceptable. Example: 'edu.ucar.unidata'.\tabularnewline
identifier\_product\_doi & string & 1 & Unassigned & digital
signature\tabularnewline
identifier\_product\_doi\_authority & string & 1 & Unassigned & digital
signature source\tabularnewline
algorithm\_version & string & 1 & & The version of the algorithm in
whatever format is selected by the developers. After the main algorithm
name and version, versions from multiple sub-algorithms may be
concatenated with semicolon separators. (ex: 'CCAST 4.2; BB emis from
MIT 2016-04-01') Must be updated with every delivery that changes
numerical results.\tabularnewline
production\_host & string & 1 & & Identifying information about the host
computer for this run. (Output of linux "uname -a"
command.)\tabularnewline
format\_version & string & 1 & v02.02.07 & Format
version.\tabularnewline
input\_file\_names & string & 1 & & Semicolon-separated list of names or
unique identifiers of files that were used to make this product. There
will always be one space after each semicolon. There is no final
semicolon.\tabularnewline
input\_file\_types & string & 1 & & Semicolon-separated list of tags
giving the role of each input file in input\_file\_names. There will
always be one space after each semicolon. There is no final
semicolon.\tabularnewline
input\_file\_dates & string & 1 & & Semicolon-separated list of creation
dates for each input file in input\_file\_names. There will always be
one space after each semicolon. There is no final
semicolon.\tabularnewline
orbitDirection & string & 1 & & Orbit is ascending and/or descending.
Values are "Ascending" or "Descending" if the entire granule fits that
description. "NorthPole" and "SouthPole" are used for polar-crossing
granules. "NA" is used when a determination cannot be
made.\tabularnewline
day\_night\_flag & string & 1 & & Data is day or night. "Day" means
subsatellite point for all valid scans has solar zenith angle less than
90 degrees. "Night" means subsatellite point for all valid scans has
solar zenith angle greater than 90 degrees. "Both" means the dataset
contains valid observations with solar zenith angle above and below 90
degrees. "NA" means a value could not be determined.\tabularnewline
AutomaticQualityFlag & string & 1 & Missing & "Passed": all spectra are
present and calibrated with no quality issues; "Suspect": at least one
spectrum is missing or calibrated with quality issues; "Failed": no
calibrated spectra; "Missing": no downlinked data.\tabularnewline
AutomaticQualityFlagExplanation & string & 1 & 'Passed': all spectra are
present and calibrated with no quality issues; 'Suspect': at least one
spectrum is missing or calibrated with quality issues; 'Failed': no
calibrated spectra; 'Missing': no downlinked data. & A text explanation
of the criteria used to set AutomaticQualityFlag; including thresholds
or other criteria.\tabularnewline
qa\_pct\_data\_missing & float & 1 & & Percentage of expected
observations that are missing.\tabularnewline
qa\_pct\_data\_geo & float & 1 & & Percentage of expected observations
that are successfully geolocated.\tabularnewline
qa\_pct\_data\_sci\_mode & float & 1 & & Percentage of expected
observations that were taken while the instrument was in science mode
and are successfully geolocated.\tabularnewline
qa\_no\_data & string & 1 & TRUE & A simple indicator of whether this is
an "empty" granule with no data from the instrument. "TRUE" or
"FALSE".\tabularnewline
title & string & 1 & 13:30 orbit L1 CHIRP & a succinct description of
what is in the dataset. (= ECS long name)\tabularnewline
summary & string & 1 & The CHIRP Level 1 product for the 13:30
sun-synchronous orbit consists of calibrated radiance spectra at a
common resolution derived from hyperspectral instruments on
EOS-Aqua\textbackslash{}, S-NPP\textbackslash{}, and JPSS-1/NOAA-20
platforms adjusted to form a continuous climate-quality record. & A
paragraph describing the dataset, analogous to an abstract for a
paper.\tabularnewline
shortname & string & 1 & SSYN1330CHIRP1\_placeholder & ECS Short
Name\tabularnewline
product\_group & string & 1 & l1\_chirp & The group name to be used for
this product when it is collected in a multi-group file type, like SNO
or calsub\tabularnewline
metadata\_link & string & 1 & http://disc.sci.gsfc.nasa.gov/ & A URL
that gives the location of more complete metadata. A persistent URL is
recommended for this attribute.\tabularnewline
references & string & 1 & & ATDB and design documents describing
processing algorithms. Can be empty.\tabularnewline
contributor\_name & string & 1 & UMBC Atmospheric Spectroscopy
Laboratory: Larrabee Strow & The names of any individuals or
institutions that contributed to the creation of this
data.\tabularnewline
contributor\_role & string & 1 & CrIS L1B Scientist & The roles of any
individuals or institutions that contributed to the creation of this
data.\tabularnewline
wnum\_delta\_lw & float & 1 & 0.625f & Difference between adjacent
wavenumbers in longwave spectrum, in cm-1\tabularnewline
wnum\_delta\_mw & float & 1 & 0.83333333333f & Difference between
adjacent wavenumbers in midwave spectrum, in cm-1\tabularnewline
wnum\_delta\_sw & float & 1 & 1.25f & Difference between adjacent
wavenumbers in shortwave spectrum, in cm-1\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{global-variables}{%
\subsection{Global Variables}\label{global-variables}}

\begin{longtable}[]{@{}llllll@{}}
\toprule
Name & Type & Dimensions & Description & Units & Ancillary
Variables\tabularnewline
\midrule
\endhead
obs\_id & string & obs & unique earth view observation identifier. &
&\tabularnewline
obs\_time\_tai93 & double & obs & earth view observation midtime for
each FOV & seconds since 1993-01-01 00:00 & bnds\tabularnewline
obs\_time\_utc & uint16 & obs, utc\_tuple & UTC earth view observation
time as an array of integers: year, month, day, hour, minute, second,
millisec, microsec & &\tabularnewline
lat & float & obs & latitude of FOV center & degrees\_north &
bnds\tabularnewline
lon & float & obs & longitude of FOV center & degrees\_east &
bnds\tabularnewline
land\_frac & float & obs & land fraction over the FOV & unitless
&\tabularnewline
surf\_alt & float & obs & mean surface altitude wrt earth model over the
FOV & m &\tabularnewline
surf\_alt\_sdev & float & obs & standard deviation of surface altitude
within the FOV & m &\tabularnewline
sun\_glint\_lat & float & obs & sun glint spot latitude at
scan\_mid\_time. Fill for night observations. & degrees\_north
&\tabularnewline
sun\_glint\_lon & float & obs & sun glint spot longitude at
scan\_mid\_time. Fill for night observations. & degrees\_east
&\tabularnewline
sol\_zen & float & obs & solar zenith angle at the center of the FOV &
degree &\tabularnewline
sol\_azi & float & obs & solar azimuth angle at the center of the FOV
(clockwise from North) & degree &\tabularnewline
sun\_glint\_dist & float & obs & Distance from the center of the
calculated sun glint spot to the center of the spot. Note that there may
not be a glint for cloudy or land cases and in ocean cases the glint can
move based on wind conditions. Fill for night observations. & m
&\tabularnewline
view\_ang & float & obs & off nadir pointing angle & degree
&\tabularnewline
sat\_zen & float & obs & satellite zenith angle at the center of the FOV
& degree &\tabularnewline
sat\_azi & float & obs & satellite azimuth angle at the center of the
FOV (clockwise from North) & degree &\tabularnewline
sat\_range & float & obs & line of sight distance between satellite and
FOV center & m &\tabularnewline
asc\_flag & ubyte & obs & ascending orbit flag: 1 if ascending, 0
descending & &\tabularnewline
subsat\_lat & float & obs & sub-satellite latitude at scan\_mid\_time &
degrees\_north &\tabularnewline
subsat\_lon & float & obs & sub-satellite longitude at scan\_mid\_time &
degrees\_east &\tabularnewline
scan\_mid\_time & double & obs & TAI93 at middle of earth scene scans &
seconds since 1993-01-01 00:00 &\tabularnewline
sat\_alt & float & obs & satellite altitude with respect to earth model
at scan\_mid\_time & m &\tabularnewline
local\_solar\_time & float & obs & local apparent solar time in hours
from midnight & hours &\tabularnewline
utc\_tuple\_lbl & string & utc\_tuple & names of the elements of UTC
when it is expressed as an array of integers
year,month,day,hour,minute,second,millisecond,microsecond &
&\tabularnewline
rad & float32 & obs, wnum & spectral radiance & mW/(m2 sr cm-1) & err,
qc\tabularnewline
synth\_frac & float32 & wnum & File mean fraction of signal that is
attributed to synthesized AIRS Level-1C values & unitless
&\tabularnewline
nedn & float32 & fov, wnum & noise equivalent differential radiance &
mW/(m2 sr cm-1) &\tabularnewline
atrack & ubyte & obs & Along-track index of Field Of Regard & unitless
&\tabularnewline
xtrack & ubyte & obs & Cross-track index of Field Of Regard & unitless &
bnds\tabularnewline
fov\_num & ubyte & obs & Field Of View number in FOR & unitless
&\tabularnewline
airs\_atrack & ubyte & obs & AIRS-like along-track index of Field Of
View & unitless &\tabularnewline
airs\_xtrack & ubyte & obs & AIRS-like cross-track index of Field Of
View & unitless &\tabularnewline
wnum & float64 & wnum & wavenumber & cm-1 & bnds\tabularnewline
\bottomrule
\end{longtable}
